\normalfont{disCOVIDer19}

### 2020-03-28 Documentation/article_4.tex
update

\documentclass[
12pt, % Main document font size
a4paper, % Paper type, use 'letterpaper' for US Letter paper
oneside, % One page layout (no page indentation)
%twoside, % Two page layout (page indentation for binding and different headers)
headinclude,footinclude, % Extra spacing for the header and footer
BCOR5mm, % Binding correction
]{scrartcl}
\usepackage[english]{babel}
\usepackage{url}
\usepackage{graphicx}
\usepackage{subcaption}
\usepackage{float}
\input{structure.tex} % Include the structure.tex file which specified the document structure and layout

\hyphenation{Fortran hy-phen-ation} % Specify custom hyphenation points in words with dashes where you would like hyphenation to occur, or alternatively, don't put any dashes in a word to stop hyphenation altogether

@@

@@

\paragraph{Population growth dynamics}
The dynamics of population was founded by Thomas Malthus in 1817 \cite{malthus1817essay} with his well known equation:

@@

\begin{equation}
P=\dfrac{KP_{0}e^{rt}}{K+P_{0}(e^{rt}-1)}
\end{equation}

@@

\paragraph{Application to the epidemiology}

@@

@@

The percentage indicator is calculated dividing the total number of Covid cases by the population of the respective region/province (the latter retrieved from Istat \cite{Istat+res0,Istat+res1}).
\begin{equation}
percentage~cases = \frac{total~cases}{local~population} \dot 100
\end{equation}
This indicator ensures that the number of cases in more populated areas are not over-indexed compared to less populated ones. Similarly, it ensures less populated areas are not under-indexed.

The density  indicator accounts for the territorial extension (in $km^2$) of regions/provinces expressed in parts per thousand (\textperthousand) and is calculated as follows:
\begin{equation}
density =  \dfrac{total~cases}{territorial~extension}\dot 1000
\end{equation}
This indicator ensures that we are not underestimating small regions/provinces with fewer cases than larger ones but with more concentrated cases per $Km^2$.

@@

\subsection{Data Inspection}

@@

>>>>

\documentclass[
12pt, % Main document font size
a4paper, % Paper type, use 'letterpaper' for US Letter paper
oneside, % One page layout (no page indentation)
%twoside, % Two page layout (page indentation for binding and different headers)
headinclude,footinclude, % Extra spacing for the header and footer
BCOR5mm, % Binding correction
]{scrartcl}
\usepackage[english]{babel}
\usepackage{url}
\usepackage{graphicx}
\usepackage{subcaption}
\usepackage{float}
\usepackage{epigraph}
\usepackage{mathcomp}
\input{structure.tex} % Include the structure.tex file which specified the document structure and layout
\sloppy
\hyphenation{Fortran hy-phen-ation} % Specify custom hyphenation points in words with dashes where you would like hyphenation to occur, or alternatively, don't put any dashes in a word to stop hyphenation altogether

@@

\newpage

\epigraph{ "The laws of history are as absolute as the laws of physics, and if the probabilities of error are greater, it is only because history does not deal with as many humans as physics does atoms, so that individual variations
count for more" (I.Asimov, Foundation and Empire) }

\newpage

@@

\subsection{Population growth dynamics}
The dynamics of population was founded by Thomas Malthus in 1817 \cite{malthus1817essay} with his well known equation:

@@

\begin{equation}
P=\dfrac{KP_{0}e^{rt}}{K+P_{0}(e^{rt}-1)}
\label{logistic_equation}
\end{equation}

@@

\subsection{Application to the epidemiology}

@@

\subsection{Time series approach}

\subsection{An ab-initio approach: the SEIR model}

@@

The percentage indicator is calculated dividing the total number of Covid cases by the population of the respective region/province (the latter retrieved from Istat \cite{Istat+res0,Istat+res1}).
\begin{equation}
percentage~cases = \frac{total~cases}{local~population} \times 100
\end{equation}
This indicator ensures that the number of cases in more populated areas are not over-indexed compared to less populated ones. Similarly, it ensures less populated areas are not under-indexed.

The density  indicator accounts for the territorial extension (in $km^2$) of regions/provinces expressed in parts per thousand (  \textperthousand ) and is calculated as follows:
\begin{equation}
density =  \dfrac{total~cases}{territorial~extension}\times 1000
\end{equation}
This indicator ensures that we are not underestimating small regions/provinces with fewer cases than larger ones but with more concentrated cases per $Km^2$.

@@

\subsection{Data Inspection}\label{Data Inspection}

@@

Panel \textit{Analysis} explores different mathematical models for shaping the infections time series, namely the ones introduced in \ref{Theoretical Background}. As previously argued, each of these models predictive power hinges on uncertain actual scenarios, such as the effectiveness of restrictive measures, the presence of several independent and spread outbreaks, and so on. Package \cite{growthcurver} has been used for growth curve fitting. This package provides function \textit{SummarizeGrowth}, which inputs the time series of sample data and outputs the model represented by the growth metrics. Such parameters include those of the logistic equation that best fit the data \ref{logistic_equation}. The reasons why this package was chosen are chiefly two: at the one hand, it performs non-linear curve fitting with the Levenberg-Marquardt algorithm \cite{more1978levenberg}, which happens to be one of the most robust non-linear least squares  (NLS) algorithms. For this step, function \cite{nlsLM} is used. On the other hand, the package is endowed with two methods for background correction.

At the top of analysis panel the user is allowed to pick one dataset among national, by region and by province. Hence, any following analysis will use the selected dataset as input (the user can browse the raw dataset in panel inspection, see \ref{Data Inspection} ). The first section is devoted to the logistic model. An input box \ref{fig:logistic_input} lists several dynamic inputs: 
\begin{itemize}

\item The date range that the calculator will use for curve fitting. The option to choose initial and final dates different from those at, resepectively, the beginning and the end of the dataset, is useful in two ways: first, it allows to cut initial dates which possibly correspond to zero or constant infections data, as a consequence of a delay in the outbreak in that territory; second, it allows to compute the availabe prediction n days ahead, by cutting the last n dates, and compare it to the real data. \item A check-box that, if selected, will use for computations and rendering the data of the share of infected among the tested, instead of the the infected themselves. That is, it will "standardise positive cases by total swabs". This may be useful to capture the "selection bias", but only in the scenario in which tests are randomly assigned to the population, or at least are assigned with a logic common to all dates and territories. This option is not currently available for provinces. \item Plot type selection boxes: should cumulative cases and fitted curve be plotted or new cases, or both (The user can always show and hide plots' components by clicking on their label in the legend).
\item Residuals plot type. Four options for graphically rendering of the residuals are available: Residuals vs. fitted values; Standardized residuals vs. fitted values; Autocorrelation; Square root of absolute residuals vs. fitted values. Output is displayed within three boxes: Inside the \textit{Plot} box \ref{fig:logistic_plot1} the sample points, the fitted logistic curve and a confidence band at 95 \% level for the logistic curve are overlayed. The user can view the sample and fitted values by hovering over or touching (for touch-screen devices) them. In addition, if \textit{new cases} is selected, a plot of sample cases differences (which correspond to new cases, in fact) is shown over the logistic estimated distribution \ref{fig:logistic_plot2}. The latter is simply obtained by deriving the right hand side of formula \ref{logistic_equation}
\end{itemize}
\begin{equation}
\dot{N}= \frac{(\frac{K-N_0}{N_0})Kre^{-rt}}{[1+(\frac{K-N_0}{N_0})e^{-rt}]^2}
\end{equation}

\begin{figure}[H]
  \centering
\begin{subfigure}{0.6\textwidth}
  % include second image
  \includegraphics[width=1\linewidth]{Figures/logistic_input.png} 
  \caption{SEM image of the virus}
  \label{fig:logistic_input}
\end{subfigure} 
\hspace{5.5cm}
\begin{subfigure}{0.6\textwidth}
  % include second image
  \includegraphics[width=1\linewidth]{Figures/logistic_plot1.png} 
  \caption{SEM image of the virus}
  \label{fig:logistic_plot1}
\end{subfigure} 
\hspace{5.5cm}
\begin{subfigure}{0.6\textwidth}
  % include second image
  \includegraphics[width=1\linewidth]{Figures/logistic_plot2.png} 
  \caption{SEM image of the virus}
  \label{fig:logistic_plot2}
\end{subfigure}
\caption{ }
\label{fig:logistic_plots_set}
\end{figure}
